Ok Then, here it is

### 2017-12-09 David Project/Paper/paper_mnras/paper.tex

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[K. T. Smith et al.]{
Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
A. N. Other,$^{2,\dagger}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country\\
$^\dagger$NuGrid collaboration}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

@@

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

@@

@@

\section{Methods, Observations, Simulations etc.}

@@

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

@@

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

An example figure can be seen in \Fig{mass-N14}.
, and tables as
e.g. \Tab{example_table}.

% Example figure
\begin{figure}
  % To include a figure from a file named example.*
  % Allowable file formats are eps or ps if compiling using latex
  % or pdf, png, jpg if compiling using pdflatex

  %\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
  \caption{This is an example figure. Captions appear below each
    figure.  Give enough detail for the reader to understand what
    they're looking at, but leave detailed discussion to the main body
    of the text.  This particular figure file will appear when you
    exectute the example notebook in
    \texttt{figs/figure\_template}. Then uncomment the
    \texttt{includegraphics} command in the latex source file.} 
    \lFig{mass-N14}
\end{figure}

@@

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{figs/figure_template/mass-O16}
    \caption{Another figure.}
    \lFig{mass-O16}
\end{figure}

@@

\bibliographystyle{mnras}
\bibliography{../paper_resources/bib/nugrid} % if your bibtex file is
                                             % called example.bib

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{subcaption}
\usepackage{graphicx}

@@

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{Ok Then, here it is}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[D. Stephens]{
David Stephens}

% These dates will be filled out by the publisher
%\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
%\pubyear{2015}

@@

% Abstract of the paper
\begin{abstract}
During the asymptotic giant branch (AGB) phase of stellar evolution for a 2\Msun~star, the periodic thermal pulses have temperatures as high as 2.9\ee{8} \K. The \neon[22]($\alpha,n$)\magnesium[25]
After the formation of the \carbon[13] pocket

This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
AGB -- Diffusion Coefficient -- Pre-solar Grains
\end{keywords}

@@

* Why problem is interesting*

- Zr ratios in pre solar grains from AGB stars show isotopic signatures of material that left the star. 
- This is from envelope and Zr is produced in 13C pocket, then readjusted in the thermal pulse
- Tracer of conditions that were in the star at that time

* what have other people done *

- battino tried varying f and how diffusion happens for effects (couldnt get ratios seen)
- barzyk for xe128 ratio

* My probelm, the gap! *

- Try a different functionality of diffusion coefficient, hydro leads to this form
- It contains lower diffusion at base of convection zone, less 22Ne reaction, less Zr96

@@

\section{Methods and Models}

@@

\subsection{\MESA Models}
\label{sec:mesa_models} % used for referring to this section from elsewhere

Only a 2\Msun, $Z=0.02$, stellar evolution model was usedd. This was computed using the \MESA~\citep{mesa} stellar code and taken from the \nugrid NuGrid set1ext, set1.2 models \citep{models}. These models were evolved from the pre-main sequence to a white dwarf. For this work, a singular thermal pulse, the 13th?, was analyzed and a Kippenhahn diagram of this particular thermal pulse can be seen in \Figure{kipp}.

For these models, the mixing lengths theory \citep{cox}, MLT, is used for the convection zones with a mixing length, $\alphaMLT=1.73$. Overshoot is implemented in \MESA with the formula from \citet{overshoot} and \citet{freytag}:

\begin{equation}
D = D_{0} exp^{-2z/f H_{p0}}
\label{eq:overshoot}
\end{equation}

Where D$_{0}$ and H$_{p0}$ are taken at the convective boundary.

\subsection{\zirconium[95] and \iodine[128] Branching}
\label{sec:branching}

\subsection{Diffusion Coefficient Modifications}
\label{sec:diffusion}

\subsection{\mppnp~Post Processing}
\label{sec:mppnp}

\subsection{Neutron Density and Temperature}
\label{sec:neutron}

\section{Results}
Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

@@

% Kippenhahn figure
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/2M_Kippenhahn.png}
  \caption{Within the He intershell region, the \carbon[13] pocket forms and isotopic ratios are set by the \spr~(\Fig{zr_ratio13C}). It is then mixed and diluted in the He-flash pulse driven convection zone where temperatures get high enough to activate \neon[22]($\alpha,n$)\magnesium[25]. This shifts the isotopic ratios to those shown in \Figure{zr_ratioDil}} 
  \lFig{kipp}
\end{figure}

% c13 pocket zr ratio
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/C13_Zr.png}
  \caption{Within the \carbon[13] pocket there is a significant amount of \zirconium[94] produced but almost no \zirconium[96]. This is due to the low neutron densities not opening the \zirconium[95] branch.} 
  \lFig{zr_ratio13C}
\end{figure}

% Zr ratio after pulse
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/Pulse_Zr.png}
  \caption{After the \carbon[13] pocket is mixed into the He-flash pulse driven convection zone, the temperatures get high enough for the \neon[22]($\alpha,n$)\magnesium[25] reaction. This provides high enough neutron densities to open the \zirconium[95] branch and boost the \zirconium[96].} 
  \lFig{zr_ratioDil}
\end{figure}

% Xe plot
\begin{figure}
	\includegraphics[width=\columnwidth]{figs/xe.png}
    \caption{Another figure.}
    \lFig{mass-O16}
\end{figure}

% Zr 95 branch
\begin{figure}
	\includegraphics[width=\columnwidth]{figs/Zr95_branch.png}
    \caption{Another figure.}
    \lFig{zr95}
\end{figure}

% Zr 94 plot
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/Zr94.png}
  \caption{This is the Zr94 mil plot \citet{zr}.} 
  \lFig{zr94}
\end{figure}

% diffusion plot
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/Diffusion_compare.png}
  \caption{This is a comparison between the diffusion coefficients} 
  \lFig{diffusion}
\end{figure}

% time scale plot
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/Time_scale.png}
  \caption{This is the time scale plot} 
  \lFig{time_scale}
\end{figure}

% neutron denisty time plot
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/Neutron_Density_Time.png}
  \caption{This is the neutron density as a function of time} 
  \lFig{density}
\end{figure}

% sub time step neutron plots
\begin{figure}
\centering
\begin{subfigure}[b]{1\columnwidth}
   \includegraphics[width=1\columnwidth]{figs/T_Neutron_sub.png}
   \lFig{neutron_sub}
\end{subfigure}

\begin{subfigure}[b]{1\columnwidth}
   \includegraphics[width=1\columnwidth]{figs/T_Neutron_Sub_Closeup}
   \lFig{neutron_sub_close}
\end{subfigure}
\caption{Testing}
\end{figure}

@@

@@

\bibliographystyle{mnras}
\bibliography{paper.bib} % if your bibtex file is
                                             % called example.bib
